The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 and with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
 based on X-ray emissions.

 The temperature profile (left column of \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 most of the region between the forward shock and the turbulent zone\
 is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

@@

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in top left panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column of \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

 To explore how the disk affect the formation of the Galactic bubbles,\
 we compare the fiducial run (leftmost column of \Cref{fig__jetI5+ismSeed3-45deg})\
 with the case adopting the smooth disc\
 (second column; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
 The results show that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (third column) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc,\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.

>>>>

 The fiducial run (leftmost column) with the initial condition specified in Section \ref{Methodology}\
 shows that the edge of the outermost bubbles is indeed a forward shock,\
 expanding 12.5 kpc above and below the Galactic plane,\
 with a semiminor axis about 6.8 kpc on the plane.\
 We note that the overall extent of the outermost bubbles is comparable to\
 the two spherical objects of a radius 6-7 kpc proposed by \citet{Predehl2020} for modeling the eROSITA bubbles\
 based on X-ray emissions.

 The temperature profile (left middle panel in \Cref{fig__profile}) along the positive z-axis in\
 \Cref{fig__jetI5+ismSeed3-45deg} indicates that\
 most of the region between the forward shock and the turbulent zone\
 is around 0.3-0.4 keV, similar to that observed by \citet{Miller2016} and \citet{Kataoka2018}.

@@

 The most interesting finding is that there is a innermost bubbles\
 (dashed box in left top panel of \Cref{fig__jetI5+ismSeed3-45deg})\
 extending out from the Galactic center on either side of the thin disk.\
 The innermost bubbles are cold (1-10 eV), dense ($10^{-4}$ -- $10^{-2}$ cm$^{-3}$),\
 and underpressured with respect to the turbulent plasma.\
 Moreover, the close-up view of profiles around $z=3.7$ kpc (right column in \Cref{fig__profile})
 demonstrates that there is a sharp pressure jump and dense shell at $z=3.61$ kpc,\
 indicating that the innermost bubbles are an expanding reverse shock.\
 We also find that the turbulent plasma is bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

@@

 To explore how the disk affect the formation of the Galactic bubbles,\
 we compare the fiducial run (first column from left in \Cref{fig__jetI5+ismSeed3-45deg})\
 with the case adopting the smooth disc\
 (second column; \Cref{fig__initial-density-profile} shows the density profile) in a stratified atmosphere.\
 The results show that the initial density distribution of the dense disc has an insignificant effect\
 on the overall dynamics of bubbles. However, the outermost bubbles arising from the smooth disc\
 in an uniform atmosphere (third column) is spherical-shape,\
 suggesting the stratification facilitates the outermost bubbles elongation significantly.\
 Also, the two rightmost columns reveal that the development of the innermost bubbles\
 is always associated with the disc, without the disc,\
 the outermost bubbles and the turbulent plasma will be oblique,\
 indicating the dense disc is crucial for\
 the symmetry of the Galactic bubbles and for the innermost bubbles formation.
